---
advisor: Prof. François Maréchal
unitname:
  faculty: School of Engineering
  institute: Mechanical Engineering
  laboratory: "Industrial Process and Energy Systems Engineering"
venv: ./venv
---




```{r setup rosmose, warning = F, results = "hide", message=F, eval=T, echo=F}
source("./rosmose-setup.R", local = knitr::knit_global())
```

```{r venvconfig, warning = F, results = "hide", message=F, eval=T, echo=F}
path <- file.path('./venv/Scripts/python.exe')
library(reticulate)

#path <- file.path('./venv/bin/python')
library(reticulate)
#use_python(path)
use_virtualenv('./venv', required=TRUE)

#use_python(path)

```

# Abstract {-}

Within an industrial dairy processing setting, the facility owner aspires to optimize both the economic and environmental efficiencies of production. To achieve this goal, PinchSim conducted a comprehensive study of the existing plant, presenting suggested improvements in this report. \
The initial phase involved a thorough thermodynamic analysis of the plant, encompassing the computation of each flow property. Additionally, a feasibility study delved into two co-products: on the one hand Rivella's production (a Swiss beverage) utilizing the revalorization of dairy waste, specifically whey, and  on the other hand biogas production recovering both whey and sludge. Subsequently, an exergy bill was formulated to assess the potential electricity recoverable from the existing plant. Pinch Analysis was then applied to identify potential recoveries, leading to cost optimizations on specific components of the installation. A Heat Exchanger Network design was executed on a subpart of the facility to mitigate the impact of penalizing utilities. Finally, an energy conversion integration was undertaken to evaluate the most advantageous technology configuration for the dairy industrial plant. \
The findings of the report reveal several key insights. Firstly, introducing Rivella as a co-product slashes installation costs by half thanks to increased selling gains. Secondly, the implementation of heat exchangers for heat recovery can reduce operational expenditures, although results vary. Thirdly, a heat exchanger network, guided by a pinch analysis, yields modest cost reductions (0.01%). Lastly, optimizing energy conversion integration is crucial to preventing exergy losses and lowering costs. \
Hence, the conclusion drawn from this study advocates for the integration of Rivella production into the existing facility, coupled with the implementation of the recommended energy conversion technologies outlined in this report.
